Designing Turk Experiments for Visual Statistical Inference

### 2013-06-12 paper_turk.tex
reorganizing the paper

@@

@@

@@

@@

\subsection{Wage Rate for the Turkers}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage. Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task. Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable. We may study this issue while we do multiple turk experiments.

\subsection{Accepting or Rejecting Payments for Turk Evaluation} In our design we keep a test lineup plot which is very easy to evaluate. The general criteria may be to reject payment when workers do not get that easy test lineup plot. Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high. So depending on only one criteria the payment should not be made. These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

\section{What do people pick, $R^2$ or p-value?} What do people pick in a lineup plot, p-value or $R^2$? To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test. Suppose we want to test the significance of the slope ( i.e.,  $H_0: \beta=0$ against $\beta \ne 0$) of a continuous covariate $X$ in  a simple linear regression model setting. Also consider $X \sim N(0,1)$. For a sample of size $n$ this gives us 
\begin{eqnarray*}
Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
\end{eqnarray*}
Now 
\begin{eqnarray*}
X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
\end{eqnarray*}

@@

\section{Performance} In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk. We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department. We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots. We can use these data to evaluate the performance of the general participants from around the world.

\section{Quality of Turk Data}

>>>>

\subsection{Test and Training Lineup} How many test lineup?

How to setup training, randomized or sequential selection of lineup for training.

Example lineup on the homepage should be of size three or four so that more than one lineup can be placed on the homepage.

\subsection{Planing the Turk Task}
Question to ask

Whether reasoning would be collected or not

Multiple or single response

Test plot added or not

Training needed or not

Feedback given after every evaluation or not

How many lineups to show

Are the lineups randomly selected?

@@

\subsection{Form Design}

@@

\subsection{Data Security and Validity} Consideration to avoid hacking

Check for invalid input

Control for missing imput

@@

\subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task.

\subsection{Accepting or Rejecting the Task} In our design we keep a test lineup plot which is very easy to evaluate. The general criteria may be to reject payment when workers do not get that easy test lineup plot. Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high. So depending on only one criteria the payment should not be made. These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

\subsection{Processing Payment}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage. Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task. Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable. We may study this issue while we do multiple turk experiments.

\subsection{Managing Worker} pay bonus, appreciate worker by sending email, block worker etc.

\section{Turk Data Quality}

In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk. We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department. We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots. We can use these data to evaluate the performance of the general participants from around the world.

@@

Time of the task may recruit from a specific geographical location

Setting up qualification may allow certain workers to do the task

Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.

\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$? To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test. Suppose we want to test the significance of the slope ( i.e.,  $H_0: \beta=0$ against $\beta \ne 0$) of a continuous covariate $X$ in  a simple linear regression model setting. Also consider $X \sim N(0,1)$. For a sample of size $n$ this gives us 
\begin{eqnarray*}
Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
\end{eqnarray*}
Now 
\begin{eqnarray*}
X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
\end{eqnarray*}

@@
